Unsupervised training of maximum-entropy models for lexical selection in rule-based machine translation

### 2015-05-03 2015-eamt-melsa/poster/2015-eamt-melsa-poster.tex
more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60211 72bbbca6-d526-0410-a7d9-f06f51895060

  \begin{itemize}
    \item Choosing the most adequate TL 
translation for an SL word from a 
set of possible translations.
    \item b
  \end{itemize}

>>>>

  \begin{itemize}
    \item Lexical selection is:
    \begin{itemize}
    \item Choosing the most adequate 
translation for a word from a 
set of possibilities.
    \end{itemize}
    \item Why unsupervised ? 
    \begin{itemize}
      \item For many language pairs, parallel corpora are not available
    \end{itemize}
    \item Why maximum entropy ? 
    \begin{itemize}
      \item Allows linguists to define features for which weights are learnt.
    \end{itemize}
  \end{itemize}
